Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-20 manuscript.Rmd

```{r Figure 1 Small Multiples, cache=TRUE}

@@

ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line(size = 1, alpha = .80) + 
     facet_wrap(~ Journal) +
     theme(strip.text.x = element_text(size = 2.5)) +
  theme_bw() + 
  theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Historical Database", "Scopus"), guide = guide_legend(title = "")) + 
  ylab("Number of Articles") + 
  xlab("\nYear") +
     annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = cp[2], size = 1, alpha = .80) + 
     annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 4) +
  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 4)

# Join with historical database
sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
    select(Year, Journal, N, Overall.N, Documents)

sm.scopus.merged-counts <- group_by(sm.scopus.merged, Journal) %>%
     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
     arrange(desc(DataBase.N))

 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
     ungroup()
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
 lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
 lab <- paste(lab1, lab2, sep="\n")
 xpos = rep(1999, 79)
 ypos = rep(180, 79)
 ldata <- data.frame(xpos, ypos, lab, Overall.N$Journal)

 titles.reduced <- unique(sm.scopus.merged$Journal)
 titles.reduced.a <- titles.reduced[1:8]

  titles.reduced.1 <- titles.reduced[1:40]
 titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
 cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

 library(grid)
 library(gridExtra)
# Plotting function    
# 
reduced.ldata <- ldata[1:8, ]

reduced.ldata$Abbrev <- factor(reduced.ldata$Abbrev, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work") )

reduced.ldata$Abbrev = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work")
reduced.smallmult.df <- sm.scopus.merged
reduced.smallmult.df$Abbrev <- reduced.smallmult.df$Journal
reduced.smallmult.df <- na.omit(reduced.smallmult.df)

reduced.smallmult.df$Abbrev <- as.factor(reduced.smallmult.df$Abbrev)
reduced.smallmult.df$Abbrev <- factor(reduced.smallmult.df$Abbrev, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work") )

new.data <- reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ]
new.data

 plotSmallMultiples.a <-  ggplot(new.data,  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Journal %in% titles.reduced.a, ], 
               aes(Year, Documents), colour = "#533c99", alpha = .80) +

     facet_wrap(~ Abbrev) + 
    geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
     # theme(plot.title = element_text(size = 19))
     # 
#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)

 plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) + 
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size = 10)) + 
     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size = 4) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 150, yend = 150, colour = "#533c99") +
     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")

plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
     aes(Year, N)) +
     geom_line(colour="#e66101") +
     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
     facet_wrap(~ Abbrev) + 
     theme_bw() +
     theme(strip.text.x = element_text(size = 12)) +  
     theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =10)) + 
     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =4) +
     ylim(c(0,225)) +
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
```

>>>>

```{r Figure 1 Small Multiples Paper}

@@

ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line(size = 1, alpha = .80) + 
     facet_wrap(~ Journal) +
  theme_bw() + 
   theme(strip.text.x = element_text(size = 12)) +
  theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Historical Database", "Scopus"), guide = guide_legend(title = "")) + 
  ylab("Number of Articles") + 
  xlab("\nYear") +
     annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = cp[2], size = 1, alpha = .80) + 
     annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 4) +
  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 4)

```{r Figure 1 Small Multiples Supplement}
